Main1

### 2019-11-04 preproc.Rmd
..

@@

set.seed(12345)
x = rbinom(1010242, size = 1, prob = .7)
#70% of data for training, 30% for testing
train = blog[x]
test = blog[!x]
```

@@

```{r}
#Load data as corpus
#VectorSource() creates character vectors
myN <- Corpus(VectorSource(news))
```

@@

1. converting everything to lower case

```{r}
myN = tm_map(myN, content_transformer(tolower))
```

2. remove punctuation

```{r}
myN = tm_map(myN, content_transformer(removePunctuation))
```

3.remove extra whitespace

```{r}
myN = tm_map(myN, content_transformer(stripWhitespace))
```

4. remove stopwords

```{r}
myN = tm_map(myN, removeWords, stopwords("english"))
```

5. remove numbers

```{r}
myN = tm_map(myN, removeNumbers)
```

remove whitespace again due to spaces of numbers
```{r}
myN = tm_map(myN, content_transformer(stripWhitespace))
```

@@

>>>>

```{r}
##orig.wd <- getwd()
##setwd("../final/en_US")
numwords <- system("wc -w *.txt", intern=TRUE)  # intern=TRUE to return output  
numlines <- system("wc -l *.txt", intern=TRUE)
numbytes <- system("wc -c *.txt", intern=TRUE)
# longest <- system("wc -L *.txt", intern=TRUE) # not working
##setwd(orig.wd)  # return to original working dir, ie. the parent of /final

# number of words for each dataset
blog.numwords <- as.numeric(gsub('[^0-9]', '', numwords[1]))
news.numwords <- as.numeric(gsub('[^0-9]', '', numwords[2]))
twit.numwords <- as.numeric(gsub('[^0-9]', '', numwords[3]))

# number of lines for each dataset
blog.numlines <- as.numeric(gsub('[^0-9]', '', numlines[1]))
news.numlines <- as.numeric(gsub('[^0-9]', '', numlines[2]))
twit.numlines <- as.numeric(gsub('[^0-9]', '', numlines[3]))

# number of bytes for each dataset
blog.numbytes <- as.numeric(gsub('[^0-9]', '', numbytes[1]))
news.numbytes <- as.numeric(gsub('[^0-9]', '', numbytes[2]))
twit.numbytes <- as.numeric(gsub('[^0-9]', '', numbytes[3]))
```

@@

set.seed(12345)
x = sample(1010242, 300000, replace = F)
#30% of data for training, 70% for testing
#due to hardware issues
train = news[x]
test = news[!x]
```

@@

```{r}
#Load data as corpus
#VectorSource() creates character vectors
myN <- Corpus(VectorSource(train))
```

@@

1. converting everything to lower case
2. remove punctuation
3.remove extra whitespace
4. remove stopwords
5. remove numbers
remove whitespace again due to spaces of numbers

```{r}
#1
myN = tm_map(myN, content_transformer(tolower))
#2
myN = tm_map(myN, content_transformer(removePunctuation))
#3
myN = tm_map(myN, content_transformer(stripWhitespace))
#4
myN = tm_map(myN, removeWords, stopwords("english"))
#5
myN = tm_map(myN, removeNumbers)
#6
myN = tm_map(myN, content_transformer(stripWhitespace))
```

@@

## high freq words

```{r}
newsTDMHighFreq = findFreqTerms(newsTDM, lowfreq = 10000, highfreq = Inf)
inspect(newsTDM[newsTDMHighFreq, 1:10 ])
newsTDMHighFreq
```

```{r}
news.freq <- row_sums(newsTDM, na.rm=TRUE)
library(ggplot2)
#top 10 words -- counts
qplot(y = news.freq[order(news.freq, decreasing = T)][1:10], x = names(x = news.freq[order(news.freq, decreasing = T)][1:10]), ylab= "Frequency", xlab = "Word", main = "The top 10 words -- counts")
```
